---
title: "dnra: do not re-assign"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dnra: do not re-assign}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dnra)
```

The `dnra` package provides a minimal approach to caching objects, intended to 
be used for long-running calculations and only at the top-level. It does this by
replacing ad hoc code like

```{r, eval = FALSE}
# complex_object <- long_computation(variables)
# saveRDS(complex_object, "complex_object.RDS")
complex_object <- readRDS("complex_object.RDS")
```

with

```{r, eval = FALSE}
complex_object %<~% long_computation(variables)
```

This avoids breaking the flow of your script while still not recomputing the
`complex_object`.

This main function, `%<~%`, in `dnra` is an alternative assignment operator 
that:
  
  - assigns and caches an object if it does not exist and has not previously been 
cached,
- loads from cache if the binding does not exist but a cache does, and
- does nothing if an object exists.

Additionally, objects assigned with `%<~%` have an attribute "run_time" that
records the length of time to compute the value. This can be extracted with
`get_runtime()`.

The intended use is in scripts that may be extended, where long calculations may
not need to be rerun, and manually saving and loading an object creates clutter.
The `dnra` package can also be used in place of R markdown caching to avoid
having to worry that changing a chunk variable or some other part of a chunk
will require re-running the two-hour model-fitting.

Objects are saved to a folder specified by `set_save_folder()`, and can be deleted
or renamed with `.delete()` or `.rename()`.


### Example

We can use `%<~%` in place of the regular assignment operator.

```{r}
set_save_folder(tempdir())
a %<~% 1 
```

If we now remove `a` and try to assign again with `%<~%` the value will be 
reloaded from the cached version.

```{r}
rm(a)
a %<~% 2
a
```

We remove `a` and delete the cache with `.delete()`

```{r}
.delete(a)
exists("a")
```

and rename with `.rename()`

```{r}
a %<~% 1
.rename(a, "b")
b
exists("a")
```

If an object exists already, then `%<~%` does not overwrite or cache:
  
```{r}
a <- 1
a %<~% 2
a
rm(a)
a %<~% 3
a
```

The run time can be extracted with `get_runtime()`.

```{r}
get_runtime(a)
```


## Warning

Since user-defined infix functions have low priority, we can get errors or
unexpected results when the RHS contains infix functions of higher priority.

```{r, eval = FALSE}
c %<~% 1 + 2 # returns 3
c # equals 1!!

.delete(c)
c %<~% (1 + 2)
c # equals 3 :)
```
